In Class Work: Pre-processed or flat data
-------------------

Listed below are a series of data files stored on the web. Figure out which type of data file each on is and how to downlaod it and open it as a data frame in R. For each one, save the result as an appropriately named `RData` file.

* School-level SAT results, New York City: 

https://data.cityofnewyork.us/api/views/f9bf-2cp4/rows.csv?accessType=DOWNLOAD

```{r}
nyc<-read_csv("https://data.cityofnewyork.us/api/views/f9bf-2cp4/rows.csv?accessType=DOWNLOAD")

save(nyc,file="nyc.Rdata")

```




* Survey of veterans data from Angrist (1993) "The Effect of Veterans Benefits on Education and Earnings"

https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/CAQYME



```{r}
sov<-read_dta("soviii_ang93b.dta")

save(sov,file="sov.Rdata")
```


* Vehicle Fuel Type Count 

https://data.ca.gov/group/transportation

```{r}
fuel<-read_csv("https://data.ca.gov/dataset/15179472-adeb-4df6-920a-20640d02b08c/resource/d304108a-06c1-462f-a144-981dd0109900/download/vehicle-fuel-type-count-by-zip-code.csv")

save(fuel,file="fuel.Rdata")

```




* World Cup 2014 Player Data
The dataset includes information about players in the World Cup 2014. 

https://opensource.indeedeng.io/imhotep/docs/sample-data/

```{r}
soccer<-read_tsv("http://indeedeng.github.io/imhotep/files/worldcupplayerinfo_20140701.tsv")

save(soccer,file="soccer.Rdata")
```



* NCES data on Average Daily Attendance (*This data needs to be converted to be tidy*): 
*don't use this one ---http://nces.ed.gov/programs/digest/d13/tables/dt13_203.90.asp---
* https://nces.ed.gov/programs/digest/d19/tables/dt19_203.90.asp


```{r}

library(tidyverse)
library(haven)
library(readxl)
library(curl) 

if(file.exists("attend.xls")==FALSE){
  download.file("https://nces.ed.gov/programs/digest/d19/tables/xls/tabn203.90.xls",destfile="attend.xls", mode="wb")
  #For windows mode="wb" must be added, because Windows uses binary files. 
attend<-read_excel("attend.xls",skip=4,col_names=FALSE)  
}else{
  attend<-read_excel("attend.xls",skip=4,col_names=FALSE)
}

if(file.exists("attend2.xls")==FALSE){
 curl_download("https://nces.ed.gov/programs/digest/d19/tables/xls/tabn203.90.xls",destfile="attend2.xls")
attend2<-read_excel("attend2.xls",skip=4,col_names=FALSE)  
}else{
 attend2<-read_excel("attend2.xls",skip=4,col_names=FALSE)
}

# For whatever reason there is error when accessing previous versions of this table, so the newest needs to be viewed and downloaded instead. Either of the above codes work 

```

