---
title: 'Regression: In Class Work'
author: "Garcia"
output:
  word_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
library(tidymodels)
library(plotly)
```

```{r}
ad<-read_rds("area_data.Rds")
```

1. Estimate a model that includes the census division (`division`)  of the area as the sole independent variable, and mobility `perc_moved in` as the dependent variable. Provide an interpretation of the results. "perc_moved_in~division"
```{r}
set.seed(35202)

split_data<-ad%>%initial_split(prop=.5)

ad_train<-training(split_data)

ad_test<-testing(split_data)


lm_fit <- 
  linear_reg() %>% 
  set_engine("lm")%>%
  set_mode("regression")


move_wf<-workflow()%>%
  add_model(lm_fit)


move_formula<-as.formula("perc_moved_in~division")


move_rec<-recipe(move_formula,data=ad)%>%
  step_dummy(division)

move_wf<-move_wf%>%
  add_recipe(move_rec)


lm_results<-fit(move_wf,ad_train)

lm_results%>%
  tidy()

lm_results%>%
  pull_workflow_fit()%>%
  glance()


ad_test<-
  predict(lm_results,ad_test)%>%
  rename(pred1=.pred)%>%
  bind_cols(ad_test)

rmse_1<-ad_test%>%rmse(truth=perc_moved_in,estimate=pred1)  
rmse_1

```


2. Add both income (`income_75`) and commute times (`perc_commute_30p`) to the above model and describe the coefficients for all three  of the variables. 
```{r}

move_formula<-as.formula("perc_moved_in~division+income_75+perc_commute_30p")


move_rec<-recipe(move_formula,data=ad)%>%
  step_dummy(division)

move_wf<-move_wf%>%
  update_recipe(move_rec)


lm_results<-fit(move_wf,ad_train)

lm_results%>%
  tidy()

lm_results%>%
  pull_workflow_fit()%>%
  glance()


ad_test<-
  predict(lm_results,ad_test)%>%
  #PLEASE NOTE: new models being fit need new pred# names, so your first is pred1, the second is pred2, the third is pred3, etc. 
  rename(pred2=.pred)%>%
  bind_cols(ad_test)

rmse_2<-ad_test%>%rmse(truth=perc_moved_in,estimate=pred2)  
rmse_2
```


3. Which of the two models above fit the data better? How do you know?

```{r}
#This is a way of comparing the models in the same table. 
rmse_comp<-rbind(rmse_1,rmse_2)
rmse_comp
```

